---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ghr

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/maurolepore/ghr.svg?branch=master)](https://travis-ci.org/maurolepore/ghr)
[![Coveralls test coverage](https://coveralls.io/repos/github/maurolepore/ghr/badge.svg)](https://coveralls.io/r/maurolepore/ghr?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/ghr)](https://cran.r-project.org/package=ghr)
<!-- badges: end -->

The ghr (GitHub-R) package helps you to request information to the GitHub-API using an intuitive syntax, similar to that of `remotes::install_github()`. For example, this is a valid path `maurolepore/ghr@master`. Also this one: `maurolepore/ghr/reference@gh-pages`.

## Installation

``` R
install.packages("devtools")
devtools::install_github("maurolepore/ghr")
```

## Example

```{r example}
library(magrittr)
library(ghr)
```

Use `ghr_get()` to get a GitHub-API response. Notice that the call is memoised.

```{r}
system.time(ghr_get("maurolepore/ghr"))
# Takes no time because the first call is memoised
system.time(ghr_get("maurolepore/ghr"))
```

Use `ghr_show_fields()` to see what fields are available for a given `path`.

```{r}
response <- ghr_get(path = "maurolepore/ghr/tests")
class(response)

ghr_show_fields(response)
```

Use `ghr_pull()` to access specific fields of the GitHub response.

```{r}
ghr_pull(response, "name")
```

Use `ghr_ls()` as a shortcut for `ghr_pull(ghr_get(owner/repo/subdir@branch), field = "path")`. It offers an interface similar to `fs::dir_ls()`.

```{r}
path <- "maurolepore/tor/inst/extdata/mixed"

# The first call make the request
system.time(ghr_ls(path))
# Takes no time because the first call is memoised
system.time(ghr_ls(path))

ghr_ls(path, regexp = "[.]csv$")
ghr_ls(path, regexp = "[.]csv$", invert = TRUE)

ghr_ls(path, regexp = "[.]RDATA$", invert = TRUE, ignore.case = FALSE)
ghr_ls(path, regexp = "[.]RDATA$", invert = TRUE, ignore.case = TRUE)
```

The `path` argument to `ghr_get()` understands a syntax as `owner/repo/path@branch`

```{r}
ghr_show_branches("maurolepore/ghr")

"maurolepore/ghr@gh-pages" %>% 
  ghr_get() %>% 
  ghr_pull("name")
```

You can pull the URLs to read or browse multiple files at once.

```{r}
"maurolepore/tor/inst/extdata/csv" %>% 
  ghr_get() %>% 
  ghr_pull("download_url") %>%
  lapply(read.csv, stringsAsFactors = FALSE)
```

```{r}
html_urls <- "maurolepore/tor/inst/extdata/csv" %>% 
  ghr_get() %>% 
  ghr_pull("html_url")
html_urls

if (interactive()) {
  html_urls %>% 
    lapply(utils::browseURL)
}
```

---

## Acknowledgements

Thanks to Gábor Csárdi et. al for the [gh package](https://github.com/maurolepore/ghr) and to Francois Michonneau, James Balamuta, Noam Ross and Bryce Mecum for sharing their ideas and code.
